### 2021-08-02 publications/2020-03-paper/revisions/changes/discussion-revised.tex
reorganises changes dir

Our policy-agnostic analysis relies on optimal solutions and scenarios. However, policy makers in Japan are considering two alternatives as to the long-term nature of the low-carbon energy system. One approach could prioritise nuclear energy and reap the benefits of inexpensive, low-carbon energy if consensus from the public for its long-term deployment and use can be achieved. Another low carbon energy pathway proposed by our results is a transition toward a hydrogen economy, utilising hydrogen as a storage medium to engender significant deployment of renewable energy. The hydrogen pathway also provides more energy security. As social opposition to nuclear power is a prominent issue in Japan, the deployment of a parallel nuclear and hydrogen-based energy system is unlikely. Nonetheless, our results indicate that these two approaches are not mutually exclusive. The cost of transitioning to a hydrogen energy system without deploying any new nuclear is much higher than that of any of the nuclear-inclusive options. Deploying nuclear in tandem with hydrogen provides a cost-effective compromise. An approach reliant on a mature technology like nuclear also improves the likelihood of Japan meeting its 2050 emission goals, as the timely success of the Japanese hydrogen plan is far from certain. At the very least, as is the case for CCS and fossil fuels, nuclear power may offer a ``bridging" option, providing a low-carbon pathway in the short-term through extended nuclear lifetimes and limited new builds, allowing sufficient time for the maturation of hydrogen and renewable-based energy options for long-term deployment. If supported politically, long-term use of nuclear power could provide emission cuts well beyond the 2050 targets. Policy which is cognizant of these economic, environmental, and social aspects of energy systems is required to deliver a low-cost, low-carbon energy future for Japan which is socially acceptable.

>>>>

Our policy-agnostic analysis relies on optimal solutions and scenarios. However, policy makers in Japan are considering two alternatives as to the long-term nature of the low-carbon energy system. One approach could prioritise nuclear energy and reap the benefits of inexpensive, low-carbon energy if consensus from the public for its long-term deployment and use can be achieved. Another low carbon energy pathway proposed by our results is a transition toward a hydrogen economy, utilising hydrogen as a storage medium to engender significant deployment of renewable energy. The hydrogen pathway also provides more energy security. As social opposition to nuclear power is a prominent issue in Japan, the deployment of a parallel nuclear and hydrogen-based energy system is unlikely. Nonetheless, our results indicate that these two approaches are not mutually exclusive. The cost of transitioning to a hydrogen energy system without deploying any new nuclear is much higher than that of any of the nuclear-inclusive options. Deploying nuclear in tandem with hydrogen provides a cost-effective compromise. An approach reliant on a mature technology like nuclear also improves the likelihood of Japan meeting its 2050 emission goals, as the timely success of the Japanese hydrogen plan is far from certain \added{especially considering the more ambitious carbon reduction goals recently announced by METI \mbox{\cite{noauthor_japans_2021,yamaguchi_japan_2021}}} . At the very least, as is the case for CCS and fossil fuels, nuclear power may offer a ``bridging" option, providing a low-carbon pathway in the short-term through extended nuclear lifetimes and limited new builds, allowing sufficient time for the maturation of hydrogen and renewable-based energy options for long-term deployment. If supported politically, long-term use of nuclear power could provide emission cuts well beyond the 2050 targets. Policy which is cognizant of these economic, environmental, and social aspects of energy systems is required to deliver a low-cost, low-carbon energy future for Japan which is socially acceptable.

### 2021-08-02 publications/2020-03-paper/revisions/changes/introduction-revised.tex
reorganises changes dir

We are probing these questions by simulating cost-optimised energy transitions in the electricity supply sector with rigid carbon constraints using a suite of existing and emerging electricity generation and storage technologies. We use Japan as a proxy for a developed nation committed to addressing climate change. However, the results have global significance. Like many other developed nations, Japan has been rapidly deploying renewables \deleted{and has attempted to transition away from nuclear power since the }  \added{, and in the wake of the }  Fukushima Daiichi accident \deleted{\mbox{
\cite{international_energy_agency_latest_2019}}. Yet Japan is also considering }  \added{, it shut down its nuclear reactors and increased its reliance on coal \mbox{\cite{international_energy_agency_latest_2019, noauthor_electricity_2019}}. However, now Japan is } reinvigorating its nuclear power sector, \added{as} evidenced by the restart of \added{some of} its nuclear reactors \cite{iaea_pris_nodate}. Additionally, Japan is actively developing plans to deploy hydrogen power under the Basic Hydrogen Strategy \cite{noauthor_basic_2017} and has shown interest in utilising \gls{CCS} \cite{meti_report_2020}. Therefore, due to Japan's similarity to other developed nations and its willingness to consider a variety of commercial and pre-commercial low-carbon technologies,  \deleted{lessons learnt from these decarbonisation simulations} \added{simulating likely transition pathways for decarbonisation of the Japanese electricity sector} could inform global energy policy \added{. Our simulations provide these insights} by delineating potential transition \deleted{pathways, identifying} \added{scenarios that consider multiple combinations of a variety of technological options, and our sensitivity analyses identify} key novel technologies  \deleted{,} and their most significant parameters.
%
%%Developed nations rich in natural resources can reduce \gls{GHG} emissions by switching to natural gas or implementing \gls{CCS} at fossil fuel plants. However, these options are often economically infeasible for developing nations, which will lead to increased emissions through greater coal use \cite{international_energy_agency_latest_2019}. Japan, a developed nation without fossil fuel resources, is likely to follow a different path to reduce emissions, evidenced by the restart of nuclear reactors and a shift towards large-scale renewable energy deployment .

The context of the Japanese transition strategy also captures the priorities, subtle limitations, and lack of specificity in other developed nations' energy transition plans. Although influenced by the Paris Agreements, Japanese energy policy is governed chiefly by the Basic Energy Plan \cite{noauthor_basic_2017}, which outlines national policy towards a new energy system for the years 2030 and 2050 cognizant of limited indigenous resources, the impact of the Fukushima incident, and external pressures on energy supplies \cite{meti_annual_2018}. The plan reaffirms Japanese benchmarks for evaluating the energy system, first and foremost, within the context of energy security, followed by economic efficiency, safety, and the environment (summarised as `3E+S'; ibid). Although the Japanese 3E+S goals and the Paris Agreement targets have some parallels, the plan does not detail how the 2050 emission reduction target of 80\% is to be met. Matsuo et. al have suggested that electrification of a number of sectors will be required to achieve the ambitious 2050 target, underpinned by low-carbon technologies \cite{matsuo_quantitative_2018}. For the power sector to achieve such a target, near-zero emissions are required, and early action utilising existing technologies is preferable to delayed action utilising future technologies \cite{ashina_roadmap_2012}. The strategies currently under consideration include reinvigorating nuclear power, deploying \gls{CCS} to fossil fuel power plants, and ushering in a hydrogen economy based on renewable energy-based electrolysis as well as hydrogen imports from abroad \cite{ashina_roadmap_2012, matsuo_quantitative_2018, noauthor_basic_2017}.

>>>>

We are probing these questions by simulating cost-optimised energy transitions in the electricity supply sector with rigid carbon constraints using a suite of existing and emerging electricity generation and storage technologies. We use Japan as a proxy for a developed nation committed to addressing climate change. However, the results have global significance. Like many other developed nations, Japan has been rapidly deploying renewables \deleted{and has attempted to transition away from nuclear power since the }  \added{, and in the wake of the }  Fukushima Daiichi accident \deleted{\mbox{
\cite{international_energy_agency_latest_2019}}. Yet Japan is also considering}  \added{, it shut down its nuclear reactors \mbox{\cite{international_energy_agency_latest_2019}} and increased its reliance on coal \mbox{\cite{noauthor_electricity_2019} }} \deleted{ \mbox{\cite{international_energy_agency_latest_2019, noauthor_electricity_2019}}}. \added{However, now Japan is} reinvigorating its nuclear power sector, \added{as} evidenced by the restart of \added{some of} its nuclear reactors \cite{iaea_pris_nodate}. Additionally, Japan is actively developing plans to deploy hydrogen power under the Basic Hydrogen Strategy \cite{noauthor_basic_2017} and has shown interest in utilising \gls{CCS} \cite{meti_report_2020}. Therefore, due to Japan's similarity to other developed nations and its willingness to consider a variety of commercial and pre-commercial low-carbon technologies,  \deleted{lessons learnt from these decarbonisation simulations} \added{simulating likely transition pathways for decarbonisation of the Japanese electricity sector} could inform global energy policy \added{. Our simulations provide these insights} by delineating potential transition \deleted{pathways, identifying} \added{scenarios that consider multiple combinations of a variety of technological options, and our sensitivity analyses identify} key novel technologies  \deleted{,} and their most significant parameters.
%
%%Developed nations rich in natural resources can reduce \gls{GHG} emissions by switching to natural gas or implementing \gls{CCS} at fossil fuel plants. However, these options are often economically infeasible for developing nations, which will lead to increased emissions through greater coal use \cite{international_energy_agency_latest_2019}. Japan, a developed nation without fossil fuel resources, is likely to follow a different path to reduce emissions, evidenced by the restart of nuclear reactors and a shift towards large-scale renewable energy deployment .

The context of the Japanese transition strategy also captures the priorities, subtle limitations, and lack of specificity in other developed nations' energy transition plans. Although influenced by the Paris Agreements, Japanese energy policy is governed chiefly by the Basic Energy Plan \cite{noauthor_basic_2017}, which outlines national policy towards a new energy system for the years 2030 and 2050 cognizant of limited indigenous resources, the impact of the Fukushima incident, and external pressures on energy supplies \cite{meti_annual_2018}. The plan reaffirms Japanese benchmarks for evaluating the energy system, first and foremost, within the context of energy security, followed by economic efficiency, safety, and the environment (summarised as `3E+S'; ibid). Although the Japanese 3E+S goals and the Paris Agreement targets have some parallels, the plan does not detail how the 2050 emission reduction target of 80\% is to be met. Matsuo et. al have suggested that electrification of a number of sectors will be required to achieve the ambitious 2050 target, underpinned by low-carbon technologies \cite{matsuo_quantitative_2018}. For the power sector to achieve such a target, near-zero emissions are required, and early action utilising existing technologies is preferable to delayed action utilising future technologies \cite{ashina_roadmap_2012}. The strategies currently under consideration include reinvigorating nuclear power, deploying \gls{CCS} to fossil fuel power plants, and ushering in a hydrogen economy based on renewable energy-based electrolysis \added{\mbox{\cite{ashina_roadmap_2012,matsuo_quantitative_2018}}} as well as hydrogen imports from abroad \added{\mbox{\cite{noauthor_basic_2017}}} \deleted{\mbox{\cite{ashina_roadmap_2012, matsuo_quantitative_2018, noauthor_basic_2017}}}.

### 2021-08-02 publications/2020-03-paper/revisions/changes/litreview-revised.tex
reorganises changes dir

The model and the approach proposed in this research uniquely build on the modelling consensus outlined in the literature review and expand the consideration of technologies by including emerging near-term alternatives, and potentially disruptive technologies post-2050. This work leverages the dynamic simulation capabilities of \gls{TIMES} \cite{loulou_etsap-tiam:_2008} by incorporating learning curves for parameters such as investment and \gls{OM} costs, efficiency, and emission coefficients. Our model incorporates not only direct emissions, but also lifecycle emissions of all conventional and emerging technologies, the latter of which is an often neglected externality. This enables a more meaningful analysis of the global warming potential of emerging technologies, as life-cycle emissions become significant when considering deep emission reductions of the order of 80\% from current levels. By modelling the Japanese electricity supply system out to the year 2100, our aim is to detail the mid- to long-term impacts of technological development and market penetration, and to identify the suite of technologies which could underpin the successful achievement of carbon reduction.

>>>>

The model and the approach proposed in this research uniquely build on the modelling consensus outlined in the literature review and expand the consideration of technologies by including emerging near-term alternatives, and potentially disruptive technologies post-2050. This work leverages the dynamic simulation capabilities of \gls{TIMES} \cite{loulou_etsap-tiam:_2008} by incorporating learning curves for parameters such as investment and \gls{OM} costs, efficiency, and emission coefficients. Our model incorporates not only direct emissions, but also lifecycle emissions of all conventional and emerging technologies, the latter of which is an often neglected externality. This enables a more meaningful analysis of the global warming potential of emerging technologies, as life-cycle emissions become significant when considering deep emission reductions of the order of 80\% from current levels. By modelling the Japanese electricity supply system out to the year 2100, our aim is to detail the mid- to long-term impacts of technological development and market penetration, and to identify the suite of technologies which could underpin the successful achievement of carbon reduction. \added{Our sensitivity analysis is another novel aspect of our research, in that it elicits important technologies and their key parameters while remaining grounded in the context of the carbon constraints and the initial conditions that are reflective of many developed nations that aim to reduce their emissions.}

### 2021-08-02 publications/2020-03-paper/revisions/changes/methods-revised.tex
reorganises changes dir

\section{Methodology} \label{method}
% what is TIMES
\subsection{TIMES Model Description}
\gls{TIMES} models dynamic energy systems and simulates transition scenarios as a mixed-integer linear optimisation problem that is subject to a primary objective function and additional constraints \cite{loulou_etsap-tiam_2008}. The generation, refinement, supply, storage, and trade of energy commodities are modelled across multiple sectors and multiple regions using a wide variety of in-built commodity and process types. Emissions can be associated with energy commodities or processes as an emission coefficient per unit commodity produced or consumed.

@@

\begin{table}[H]
\centering
	\caption{Electricity demand increase over the simulation time frame.}
	\vspace{0.1in}
	\begin{tabularx}{0.4\textwidth}{p{0.15\textwidth} p{0.25\textwidth}}
		\hline
\textbf{Year} & \textbf{Annual demand} \\
 & \textbf{increase} \\
\hline
2017-2030 & 1.7 \% \cite{noauthor_electricity_2019} \\
2031-2050 & 1.0 \% \\
2051-2070 & 0.5 \% \\
2070-2100 & 0.0 \% \\
\hline 
	\end{tabularx}
\label{demand}
\end{table}

@@

While Japanese electricity demand is expected to grow in the near future  \cite{noauthor_electricity_2019}, long-term electricity demand in Japan is expected to plateau, or even decrease, due to Japan's ageing population. However, precisely quantifying this rate of decrease is challenging, as this reduction in population will likely be accompanied by increased electrification of transportation and industrial sectors. Hence, post-2030, we have assumed a demand curve based on increased electrification driving increasing demand, which eventually plateaus due to the aforementioned expected demographic changes. The model captures the initial condition of the post-Fukushima Japanese electricity supply system using The Energy Data and Modelling Centre's data from 2013-2016 \cite{the_institute_of_energy_economics_japan_energy_2018}. Long term impacts of factors such as the retirement of the existing nuclear reactor fleet and the deployment of emerging technology is assessed by simulating the system until 2100. We account for the carbon cost of each technology using an emission coefficient that incorporates both direct emissions and life cycle emissions averaged over the entire operating lifetime for each technology. Using \gls{TIMES} day-night and seasonal time periods \cite{loulou_etsap-tiam_2008}, the daily and seasonal variability of renewables is incorporated. The availability of renewables varies during these time periods based on the annually averaged capacity factors of renewables in Japan \cite{the_institute_of_energy_economics_japan_energy_2018, irena_renewable_2020}.

@@

All hydrogen storage devices are operated with a maximum availability factor of 90\%, making them extremely flexible for load-following. Long-term storage of hydrogen is also available using hydrogen tanks with appropriate loss factors \cite{iea_technology_2015}. For hydrogen electrolysers and fuel cells, life-cycle emissions from just the stack are considered, as balance-of-plant emissions from utility scale hydrogen depend strongly on the type of plant and the source of energy used for electrolysis. Our assumptions about the reduction in the investment costs and life-cycle emissions of batteries are conservative due to the rising cost of cobalt and nickel, and lithium-ion battery manufacturing being concentrated in high \gls{GHG}-emitting nations, respectively \cite{oliveira_environmental_2015,emilsson_lithium-ion_2019,turcheniuk_ten_2018,simon_potential_2015}.

>>>>

\section{Methodology} \label{method}
% what is TIMES
\subsection{TIMES Model Description}
\gls{TIMES} models dynamic energy systems and simulates transition scenarios as a mixed-integer linear optimisation problem that is subject to a primary objective function and additional constraints
\cite{loulou_etsap-tiam:_2008} . The generation, refinement, supply, storage, and trade of energy commodities are modelled across multiple sectors and multiple regions using a wide variety of in-built commodity and process types. Emissions can be associated with energy commodities or processes as an emission coefficient per unit commodity produced or consumed.

@@

\begin{table}[H]
\centering
	\caption{Electricity demand increase over the simulation time frame. \added{The demand for 2017-2030 is obtained from \mbox{
\cite{noauthor_electricity_2019}}
, the rest of the curve is based on estimated population growth trends.} }
	\vspace{0.1in}
	\begin{tabularx}{0.4\textwidth}{p{0.15\textwidth} p{0.25\textwidth}}
		\hline
\textbf{Year} & \textbf{Annual demand} \\
 & \textbf{increase} \\
\hline
2017-2030 & 1.7 \% \deleted{\mbox{
\cite{noauthor_electricity_2019} }
} \\
2031-2050 & 1.0 \% \\
2051-2070 & 0.5 \% \\
2070-2100 & 0.0 \% \\
\hline 
	\end{tabularx}
\label{demand}
\end{table}

@@

While Japanese electricity demand is expected to grow in the near future  \cite{noauthor_electricity_2019}, long-term electricity demand in Japan is expected to plateau, or even decrease, due to Japan's ageing population. However, precisely quantifying this rate of decrease is challenging, as this reduction in population will likely be accompanied by increased electrification of transportation and industrial sectors. Hence, post-2030, we have assumed a demand curve based on increased electrification driving increasing demand, which eventually plateaus due to the aforementioned expected demographic changes. The model captures the initial condition of the post-Fukushima Japanese electricity supply system using \added{historical data} The Energy Data and Modelling Centre's data from 2013-2016 \cite{the_institute_of_energy_economics_japan_energy_2018}. Long term impacts of factors such as the retirement of the existing nuclear reactor fleet and the deployment of emerging technology is assessed by simulating the system until 2100. Using \gls{TIMES} day-night and seasonal time periods
\cite{loulou_etsap-tiam:_2008}, the daily and seasonal variability of renewables is incorporated. The availability of renewables varies during these time periods based on the annually averaged capacity factors of renewables in Japan\mbox{\cite{the_institute_of_energy_economics_japan_energy_2018, irena_renewable_2020}}.

We account for the carbon cost of each technology using an emission coefficient that incorporates both direct emissions and life cycle emissions averaged over the entire operating lifetime for each technology. Using day-night and seasonal time periods\cite{loulou_etsap-tiam:_2008}, the daily and seasonal variability of renewables is incorporated. The availability of renewables varies during these time periods based on the annually averaged capacity factors of renewables in Japan \mbox{\cite{the_institute_of_energy_economics_japan_energy_2018, irena_renewable_2020}}. \added{The emission coefficient data and their sources are listed in Table \ref{eco}. The emission coefficients vary dynamically for technologies that have projections available in literature, and are linearly interpolated between available data points until the last available projection, beyond which they are held constant. For hydrogen fuel cells and electrolysers, emission coefficients vary in magnitude across different technologies but the learning curves follow similar trajectories due to the similarity of technologies \mbox{\cite{iea_technology_2015} } \mbox{\cite{pinaud_technical_2013}}. The lifecycle emissions for \gls{PWS} are unknown, hence we have assumed them to be the same as that of \glspl{SOEC} as both are lab-scale technologies with similar deployment time-frames, and \gls{PWS} must have similar or lower life-cycle emissions as \gls{SOEC} to be competitive}.

@@

All hydrogen storage devices are operated with a maximum availability factor of 90\%, making them extremely flexible for load-following. Long-term storage of hydrogen is also available using hydrogen tanks with appropriate loss factors \cite{iea_technology_2015}. For hydrogen electrolysers and fuel cells, life-cycle emissions from just the stack are considered \added{(see Table \ref{eco})} , as balance-of-plant emissions from utility scale hydrogen depend strongly on the type of plant and the source of energy used for electrolysis. Our assumptions about the reduction in the investment costs and life-cycle emissions of batteries are conservative due to the rising cost of cobalt and nickel, and lithium-ion battery manufacturing being concentrated in high \gls{GHG}-emitting nations, respectively \cite{oliveira_environmental_2015,emilsson_lithium-ion_2019,turcheniuk_ten_2018,simon_potential_2015}.

### 2021-08-02 publications/2020-03-paper/revisions/changes/results-revised.tex
reorganises changes dir

The transition simulations' results are shown in Figures \ref{scen1}-\ref{scen5}, and summarised in Table \ref{tab:results_summary} (see Table \ref{scen-table} for scenario definitions). The results of each scenario are reported as annually aggregated plots of (i) the electricity that is directly supplied to the end user, (ii) the active nameplate capacities of generation and storage technologies, and (iii) the resulting emissions (direct and life cycle) from each technology. The first plot of each scenario shows a large degree of variation as generated electricity is diverted from multiple sources to storage technologies instead of being supplied directly to the end user. The output of some technologies also varies due to their ability to load-follow. The second plot describes the transitions in terms of capacities, highlighting the effect of the capacity factor of intermittent versus base-load technologies. The third plot details the sources of direct and averaged life-cycle emissions from each source.

@@

In Scenario 1 (Figure \ref{scen1}), the model is able to meet 2030 emission goals but fails to achieve the 2050 target by a margin of 25 Mt. Emissions continue to increase by another 25 Mt by 2100, primarily due to life cycle emissions from lithium-ion storage. As in all other scenarios, coal and oil must be retired by 2030. Natural gas sees rapid growth in the near-term, but complete retirement by 2055. Once deep emission cuts have been achieved, new natural gas is deployed again from 2071 onwards for its load-following capabilities. All existing nuclear power plants must be restarted by 2022 at full operating capacity. With renewable energy as the only option for decarbonisation, significant investments in solar, onshore wind, offshore wind (both fixed-bottom and floating), and lithium-ion storage are necessary. The presence of a large share of renewables results in significant overgeneration of electricity during some years. The amount of electricity diverted to storage technologies over the entire simulation time frame is 46,342 TWh, primarily from solar (36\%), onshore wind (22\%), fixed-bottom offshore wind (22\%),and floating offshore wind (12\%). The total cost of this transition is \textbf{3.51 trillion USD}.

@@

With the availability of new nuclear reactors in Scenario 2 (Figure \ref{scen2}), both 2030 and 2050 emission targets are achieved, and a further emission reduction of 12 Mt occurs by 2100. The model chooses to rapidly deploy nuclear power plants at the maximum allowed growth rate despite the high investment cost of nuclear due to its low life-cycle emissions. This nuclear-driven reduction in emissions allows natural gas power plants to operate until 2100. The share of renewables deployed during this transition reduces dramatically. This, combined with the load-following capabilities of natural gas plants and nuclear reactors, drastically decreases the capacity of lithium-ion storage deployed. 12,220 TWh of electricity is diverted to storage, primarily from nuclear (46\%), solar (41\%), and onshore wind (8\%). The total transition cost of this scenario is the lowest, at \textbf{2.66 trillion USD.}

@@

Using emerging technologies without new nuclear power (Figure \ref{scen3}), the model is able to meet both the 2030 and 2050 emission reduction goals, but no further decarbonisation occurs after 2050. The results highlight the need to restart Japan's existing nuclear power plants at full capacity by 2030 in such a scenario. The deep emission cuts achieved through renewables, hydrogen, and \gls{CCS} allow the model to keep using \gls{lng} until 2100. Expansion of solar and onshore wind, along with a modest deployment of lithium-ion batteries and natural gas with \gls{CCS}, helps the model meet 2030 emission goals. After that, the model relies primarily on renewables and hydrogen to curb emissions. Rapid investment in hydrogen storage from 2030 onwards allows effective utilisation of renewables and precludes investment in offshore floating wind power. \gls{lng}-based \gls{CCS} plays a modest role as an intermediate technology before the model can complete the transition to utility-scale hydrogen. Between 2032-2077, the model generates 2,328 TWh  of electricity from \gls{CCS} technology, which is 2\% of the electricity generated over the entire simulation time frame. This results in 872 Mt of CO$_2$ being captured, which is well within the estimated 156 Gt CO$_2$ reservoir limit for Japan \cite{kato_energy_2016}. As the existing photovoltaic technology approaches the end of its lifetime and emerging solar technologies become cheaper and more efficient, they rapidly replace existing solar power, benefiting from the existing solar manufacture and supply chains. A total of 43,879 TWh of generated electricity is diverted to storage, primarily from solar and emerging solar technologies (48\%), fixed bottom offshore wind (28\%), and onshore wind (20\%). Much of this is used to generate 35,478 TWh worth of hydrogen, initially from alkaline electrolysis(1\%), but rapidly transitioning to PEM electrolysis (99\%) due to its greater efficiency and increasing cost-effectiveness. The cost of this transition is \textbf{3.19 trillion USD}.

@@

Deploying both emerging technologies with new nuclear reactors (Figure \ref{scen4}) results in rapid decarbonisation. Both 2030 and 2050 emission targets are met, and an additional emissions reduction of 32 Mt occurs by 2100. The deployment of 50 MW nuclear obviates the need to invest in offshore wind, lithium-ion storage, and \gls{CCS}. Hydrogen plays a significant role in decarbonisation, but it is deployed from 2035 onwards instead of 2030, as in Scenario 3. The amount of electricity diverted to storage technologies is 29,733 TWh, primarily from solar and emerging solar technologies (62\%), onshore wind (20\%), and nuclear (13\%). From this, 24,264 TWh of hydrogen is generated, produced entirely from PEM electrolysis, as there was no urgency to deploy \gls{AEC} as in Scenario 3. The cost of this transition is \textbf{2.80 trillion USD}.

@@

The fifth scenario's results (Figure \ref{scen5}) closely resemble those of the third scenario (Figure \ref{scen3}). However, \gls{SOEC}s rapidly replace a large fraction of ageing \gls{PEMEC}s, starting from 2055. Some \gls{PEMEC}s remain in the mix until 2100 despite their lower efficiency due to their lower cost. Both 2030 and 2050 emission targets are met, but no additional emission reductions occur beyond 2050. The amount of electricity diverted to storage technologies is 41,752 TWh, primarily from solar and emerging solar technologies (48\%), onshore wind (28\%), and fixed-bottom offshore wind (20\%). From this, 35,550 TWh of hydrogen is generated, mostly from \gls{SOEC} (56\%), and \gls{PEMEC} (43\%). \gls{AEC} contributes a mere 0.95\% of the total hydrogen, and \gls{PWS} plays the smallest role at 0.05\%. The cost of this transition is \textbf{3.18 trillion USD}.

>>>>

The transition simulations' results are shown in Figures \ref{scen1}-\ref{scen5}, and summarised in Table \ref{tab:results_summary} (see Table \ref{scen-table} for scenario definitions). \added{Note that the years 2013-2016 represent the initial condition modelled using historical data \mbox{
\cite{the_institute_of_energy_economics_japan_energy_2018}}
, and the simulation results begin from 2017 onwards. } The results of each scenario are reported as annually aggregated plots of (i) the electricity that is directly supplied to the end user, (ii) the active nameplate capacities of generation and storage technologies, and (iii) the resulting emissions (direct and life cycle) from each technology. The first plot of each scenario shows a large degree of variation as generated electricity is diverted from multiple sources to storage technologies instead of being supplied directly to the end user. The output of some technologies also varies due to their ability to load-follow. The second plot describes the transitions in terms of capacities, highlighting the effect of the capacity factor of intermittent versus base-load technologies. The third plot details the sources of direct and averaged life-cycle emissions from each source.

@@

In Scenario 1 (Figure \ref{scen1}), the model is able to meet 2030 emission goals but fails to achieve the 2050 target by a margin of 25 Mt. Emissions continue to increase by another 25 Mt by 2100, primarily due to life cycle emissions from lithium-ion storage. As in all other scenarios, coal and oil must be retired by 2030. Natural gas sees rapid growth in the near-term, but complete retirement by 2055. Once deep emission cuts have been achieved, new natural gas is deployed again from 2071 onwards for its load-following capabilities. All existing nuclear power plants must be restarted by 2022 at full operating capacity. With renewable energy as the only option for decarbonisation, significant investments in solar, onshore wind, offshore wind (both fixed-bottom and floating), and lithium-ion storage are necessary. The presence of a large share of renewables results in significant overgeneration of electricity during some years. The amount of electricity diverted to storage technologies over the entire simulation time frame is 46,342 TWh, primarily from solar (36\%), onshore wind (22\%), fixed-bottom offshore wind (22\%),and floating offshore wind (12\%). The total cost of this transition is \deleted{\textbf{3.51 trillion USD}}
 \added{3.51 trillion USD}.

@@

With the availability of new nuclear reactors in Scenario 2 (Figure \ref{scen2}), both 2030 and 2050 emission targets are achieved, and a further emission reduction of 12 Mt occurs by 2100. The model chooses to rapidly deploy nuclear power plants at the maximum allowed growth rate despite the high investment cost of nuclear due to its low life-cycle emissions. This nuclear-driven reduction in emissions allows natural gas power plants to operate until 2100. The share of renewables deployed during this transition reduces dramatically. This, combined with the load-following capabilities of natural gas plants and nuclear reactors, drastically decreases the capacity of lithium-ion storage deployed. 12,220 TWh of electricity is diverted to storage, primarily from nuclear (46\%), solar (41\%), and onshore wind (8\%). The total transition cost of this scenario is the lowest, at \deleted{\textbf{2.66 trillion USD.}} \added{2.66 trillion USD.}

@@

Using emerging technologies without new nuclear power (Figure \ref{scen3}), the model is able to meet both the 2030 and 2050 emission reduction goals, but no further decarbonisation occurs after 2050. The results highlight the need to restart Japan's existing nuclear power plants at full capacity by 2030 in such a scenario. The deep emission cuts achieved through renewables, hydrogen, and \gls{CCS} allow the model to keep using \gls{lng} until 2100. Expansion of solar and onshore wind, along with a modest deployment of lithium-ion batteries and natural gas with \gls{CCS}, helps the model meet 2030 emission goals. After that, the model relies primarily on renewables and hydrogen to curb emissions. Rapid investment in hydrogen storage from 2030 onwards allows effective utilisation of renewables and precludes investment in offshore floating wind power. \gls{lng}-based \gls{CCS} plays a modest role as an intermediate technology before the model can complete the transition to utility-scale hydrogen. Between 2032-2077, the model generates 2,328 TWh  of electricity from \gls{CCS} technology, which is 2\% of the electricity generated over the entire simulation time frame. This results in 872 Mt of CO$_2$ being captured, which is well within the estimated 156 Gt CO$_2$ reservoir limit for Japan \cite{kato_energy_2016}. As the existing photovoltaic technology approaches the end of its lifetime and emerging solar technologies become cheaper and more efficient, they rapidly replace existing solar power, benefiting from the existing solar manufacture and supply chains. A total of 43,879 TWh of generated electricity is diverted to storage, primarily from solar and emerging solar technologies (48\%), fixed bottom offshore wind (28\%), and onshore wind (20\%). Much of this is used to generate 35,478 TWh worth of hydrogen, initially from alkaline electrolysis(1\%), but rapidly transitioning to PEM electrolysis (99\%) due to its greater efficiency and increasing cost-effectiveness. The cost of this transition is \deleted{{3.19 trillion USD}} \added{3.19 trillion USD}.

@@

Deploying both emerging technologies with new nuclear reactors (Figure \ref{scen4}) results in rapid decarbonisation. Both 2030 and 2050 emission targets are met, and an additional emissions reduction of 32 Mt occurs by 2100. The deployment of 50 MW nuclear obviates the need to invest in offshore wind, lithium-ion storage, and \gls{CCS}. Hydrogen plays a significant role in decarbonisation, but it is deployed from 2035 onwards instead of 2030, as in Scenario 3. The amount of electricity diverted to storage technologies is 29,733 TWh, primarily from solar and emerging solar technologies (62\%), onshore wind (20\%), and nuclear (13\%). From this, 24,264 TWh of hydrogen is generated, produced entirely from PEM electrolysis, as there was no urgency to deploy \gls{AEC} as in Scenario 3. The cost of this transition is \deleted{\textbf{2.80 trillion USD}} \added{2.80 trillion USD} .

@@

The fifth scenario's results (Figure \ref{scen5}) closely resemble those of the third scenario (Figure \ref{scen3}). However, \gls{SOEC}s rapidly replace a large fraction of ageing \gls{PEMEC}s, starting from 2055. Some \gls{PEMEC}s remain in the mix until 2100 despite their lower efficiency due to their lower cost. Both 2030 and 2050 emission targets are met, but no additional emission reductions occur beyond 2050. The amount of electricity diverted to storage technologies is 41,752 TWh, primarily from solar and emerging solar technologies (48\%), onshore wind (28\%), and fixed-bottom offshore wind (20\%). From this, 35,550 TWh of hydrogen is generated, mostly from \gls{SOEC} (56\%), and \gls{PEMEC} (43\%). \gls{AEC} contributes a mere 0.95\% of the total hydrogen, and \gls{PWS} plays the smallest role at 0.05\%. The cost of this transition is \deleted{\textbf{3.18 trillion USD}} \added{3.18 trillion USD}.
